Dissertation reading notes

### 2023-11-25 Texfiles/Notes.tex
Couple of changes
trying own fstat

\section{Personal notes}

@@

>>>>

\section{Lee and Lemiuex}
\begin{itemize}
      \item Hahn, Todd, and van der Klaauw (2001) -- more theoretical
      \item RD should be seen as a data generating process rather than a method
            (i.e IV is a method, RCT is a data generating process)

      \item We want to test for covariates around the cutoff, and we want to
            test for density. In my setting we can't really test for density since
            this will be impacted by sample sizes, but we can test for
            covariates which I haven't really done poperly.

      \item McCrary (2008) looks like I should read this as well.
\end{itemize}

\section{Personal notes}
\subsection{2023-11-25}
\begin{itemize}
      \item RV is retirement year
      \item First thing is to run a proper covariate balance test.
      \item the re-run all specs
      \item then rewrite the results
      \item add in some discussion of cohort affects
      \item then think about using an instrument for retirement year
      \item then write out the two period models for standard lifecycle,
            pessimisitic survival and bequests
      \item
\end{itemize}

\subsection{2023-11-15}
\begin{itemize}
      \item Making a list of things to change and update.
      \item Regressions -- I need to add the RV into the regression equations. I
            guess I am actually a bit confused at what I think the RV is -- did
            I use expected retirement age? I used retirement year.

      \item I need to make the case that retirement is sticky?
      \item I need to add retirement year as a RV -- this is a first order
            mistake I think.

      \item Can I IV for retirement as well? What would this look like? using
            predicted retirement year as the running variable.

@@

% \subsection{Rough plan} \begin{itemize} \item Intro \begin{enumerate} \item
% "Latest data from HM Revenue Customs (published in April) showed more than
% £45bn has been taken from pots since 2015."
% https://www.ftadviser.com/pensions/2022/02/08/pension-freedoms-were-they-really-a-good-idea/
% \item what portion of savings are because of retirement savings? \item Also
% talk about heterogeneity across countries. Some countries want to move towards
% more annuitisation. This annual review is a good source of info
% \cite{banks_crawford_ar_2022} \item
% https://www.moneysavingexpert.com/savings/pension-freedom/
